Power to the Stimuli: Not the Effect

### 2022-07-21 manuscript_draft.Rmd
adding information about residuals

```{r setup, include = FALSE}
set.seed(895893)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
```

@@

@@

>>>>

```{r setup, include = FALSE}
set.seed(895893)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
library(nlme)
library(MuMIn)
```

@@

```{r test-assume, include = F, echo = F}
resid_model <- scale(residuals(user_model3))
fit_model <- scale(fitted.values(user_model3))
hist(resid_model)
qqnorm(resid_model); abline(0,1)
plot(fit_model, resid_model); abline(v = 0); abline(h = 0)

# user_model_lme <- lme(new_sample ~ sample_size + sd_item + original_n, 
#                       data = summary_long, 
#                       random = list(~1|scale2, ~scale2|power, ~scale2|name))
# r.squaredGLMM(user_model_lme)
# resid_model <- scale(residuals(user_model_lme))
# fit_model <- scale(fitted.values(user_model_lme))
# hist(resid_model)
# qqnorm(resid_model); abline(0,1)
# plot(fit_model, resid_model); abline(v = 0); abline(h = 0)
```

@@

```{r test-decile, include = F, echo = F}
resid_model <- scale(residuals(by_cutoff[["Decile 50"]]))
fit_model <- scale(fitted.values(by_cutoff[["Decile 50"]]))
hist(resid_model)
qqnorm(resid_model); abline(0,1)
plot(fit_model, resid_model); abline(v = 0); abline(h = 0)

# by scale, power, source
separate_lms <- list()
R2_lms <- list()

for (scale_loop in unique(summary_long$scale)){
  for (power_loop in unique(summary_long$power)){
    for (source_loop in unique(summary_long$source)){
      temp <- summary_long %>% 
        filter(scale == scale_loop) %>% 
        filter(power == power_loop) %>% 
        filter(source == source_loop) %>% 
        filter(name == "Decile 50")

      separate_lms[[paste(scale_loop, power_loop, source_loop, sep = "_")]] <- lm(new_sample ~ sample_size + sd_item + original_n, data = temp)
      R2_lms[[paste(scale_loop, power_loop, source_loop, sep = "_")]] <- summary(separate_lms[[paste(scale_loop, power_loop, source_loop, sep = "_")]])$r.squared
    }
  }
}

# resid_model <- scale(residuals(separate_lms[[10]]))
# fit_model <- scale(fitted.values(separate_lms[[10]]))
# hist(resid_model)
# qqnorm(resid_model); abline(0,1)
# plot(fit_model, resid_model); abline(v = 0); abline(h = 0)
```
